---
title: "Mean, bias, and MSE tables"
author: "Paulina von Stackelberg"
date: "2 5 2021"
output: html_document
---

In this document, you can find the script used to calculate the bias, MSE, and means.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}

library(tidyverse)
library(xtable)

```


Load the datasets you want to analyze - for ridge regression, lasso regression, and the two missingness proportions (0.25, 0.75).
Below I load the datasets that allow you to reproduce the tables found in the thesis, but these can be replaced by the other conditions. In the manuscript, I discuss the evaluation measures as well as outliers.

```{r load datasets}

MAR_5_lasso20 <- readRDS("MAR_5_lasso")
MAR_7_lasso20 <- readRDS("MAR_7_lasso")

MAR_5_ridge20 <- readRDS("MAR_5_ridge")
MAR_7_ridge20 <- readRDS("MAR_7_ridge")

```

## Bias

In the following chunks, bias calculations conform the description in the manuscript are performed.

```{r bias lasso}

# prop 0.25


complete_MAR5_lasso <- MAR_5_lasso20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.matrix(.,) 


cond1_MAR5_lasso <- MAR_5_lasso20[["Results_cond1"]]%>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .) %>% as.matrix(.,) 


cond2_MAR5_lasso <- MAR_5_lasso20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.matrix(.,) 


cond3_MAR5_lasso <- MAR_5_lasso20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.matrix(.,) 


cond4_MAR5_lasso <- MAR_5_lasso20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.matrix(.,) 

bias1 <- t(data.matrix(colMeans(cond1_MAR5_lasso - complete_MAR5_lasso)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(y)", model = "LASSO", mis_prop = 0.25)
bias2 <- t(data.matrix(colMeans(cond2_MAR5_lasso - complete_MAR5_lasso)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(-y)", model = "LASSO", mis_prop = 0.25)
bias3 <- t(data.matrix(colMeans(cond3_MAR5_lasso - complete_MAR5_lasso)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVreuse", model = "LASSO", mis_prop = 0.25)
bias4 <- t(data.matrix(colMeans(cond4_MAR5_lasso - complete_MAR5_lasso)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVsep", model = "LASSO", mis_prop = 0.25)

bias_25lasso <- rbind(bias1, bias2, bias3, bias4)

# prop 0.75

complete_MAR7_lasso <- MAR_7_lasso20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.matrix(.,) 


cond1_MAR7_lasso <- MAR_7_lasso20[["Results_cond1"]]%>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond2_MAR7_lasso <- MAR_7_lasso20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond3_MAR7_lasso <- MAR_7_lasso20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .) %>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond4_MAR7_lasso <- MAR_7_lasso20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .) %>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)

bias1 <- t(data.matrix(colMeans((cond1_MAR7_lasso - complete_MAR7_lasso), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(y)", model = "LASSO", mis_prop = 0.75)
bias2 <- t(data.matrix(colMeans((cond2_MAR7_lasso - complete_MAR7_lasso), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(-y)", model = "LASSO", mis_prop = 0.75)
bias3 <- t(data.matrix(colMeans((cond3_MAR7_lasso - complete_MAR7_lasso), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVreuse", model = "LASSO", mis_prop = 0.75)
bias4 <- t(data.matrix(colMeans((cond4_MAR7_lasso - complete_MAR7_lasso), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVsep", model = "LASSO", mis_prop = 0.75)

bias_75lasso <- rbind(bias1, bias2, bias3, bias4)

bias_2575_lasso <- rbind(bias_25lasso, bias_75lasso)%>% select(c("model","mis_prop","cond","AUC", "brier", "sens", "spec", "cal_b0", "cal_b1", "CoxSnell", "sens_selection", "spec_selection")) 

```

```{r bias ridge}

# prop 0.25

complete_MAR5_ridge <- MAR_5_ridge20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.matrix(.,) 


cond1_MAR5_ridge <- MAR_5_ridge20[["Results_cond1"]]%>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA)) %>% as.matrix(.,) 


cond2_MAR5_ridge <- MAR_5_ridge20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,) 


cond3_MAR5_ridge <- MAR_5_ridge20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,) 


cond4_MAR5_ridge <- MAR_5_ridge20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,) 

bias1 <- t(data.matrix(colMeans(cond1_MAR5_ridge - complete_MAR5_ridge)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(y)", model = "ridge", mis_prop = 0.25)
bias2 <- t(data.matrix(colMeans(cond2_MAR5_ridge - complete_MAR5_ridge)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(-y)", model = "ridge", mis_prop = 0.25)
bias3 <- t(data.matrix(colMeans(cond3_MAR5_ridge - complete_MAR5_ridge)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVreuse", model = "ridge", mis_prop = 0.25)
bias4 <- t(data.matrix(colMeans(cond4_MAR5_ridge - complete_MAR5_ridge)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVsep", model = "ridge", mis_prop = 0.25)

bias_25ridge <- rbind(bias1, bias2, bias3, bias4)

# prop 0.75

complete_MAR7_ridge <- MAR_7_ridge20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.matrix(.,) 


cond1_MAR7_ridge <- MAR_7_ridge20[["Results_cond1"]]%>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond2_MAR7_ridge <- MAR_7_ridge20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond3_MAR7_ridge <- MAR_7_ridge20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .) %>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA)) %>%as.matrix(.,)


cond4_MAR7_ridge <- MAR_7_ridge20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .) %>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% as.matrix(.,)

bias1 <- t(data.matrix(colMeans((cond1_MAR7_ridge - complete_MAR7_ridge), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(y)", model = "ridge", mis_prop = 0.75)
bias2 <- t(data.matrix(colMeans((cond2_MAR7_ridge - complete_MAR7_ridge), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(-y)", model = "ridge", mis_prop = 0.75)
bias3 <- t(data.matrix(colMeans((cond3_MAR7_ridge - complete_MAR7_ridge), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVreuse", model = "ridge", mis_prop = 0.75)
bias4 <- t(data.matrix(colMeans((cond4_MAR7_ridge - complete_MAR7_ridge), na.rm=T))) %>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVsep", model = "ridge", mis_prop = 0.75)

bias_75ridge <- rbind(bias1, bias2, bias3, bias4)


bias_2575_ridge <- rbind(bias_25ridge, bias_75ridge)%>% select(c("model","mis_prop","cond","AUC", "brier", "sens", "spec", "cal_b0", "cal_b1", "CoxSnell", "sens_selection", "spec_selection")) 

```

```{r table bias}

bias2575lr <- rbind(bias_2575_lasso,bias_2575_ridge) 

```

## MSE

In the following chunks, the MSE is calculated.

```{r lasso mse}

# n = 200, mis = 0.25

complete_MAR5_lasso <- MAR_5_lasso20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.matrix(.,) 


cond1_MAR5_lasso <- MAR_5_lasso20[["Results_cond1"]]%>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .) %>% as.matrix(.,) 


cond2_MAR5_lasso <- MAR_5_lasso20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.matrix(.,) 


cond3_MAR5_lasso <- MAR_5_lasso20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.matrix(.,) 


cond4_MAR5_lasso <- MAR_5_lasso20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.matrix(.,) 

MSE1 <- t(data.matrix(colMeans((cond1_MAR5_lasso - complete_MAR5_lasso)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(y)", model = "LASSO", mis_prop = 0.25)
MSE2 <- t(data.matrix(colMeans((cond2_MAR5_lasso - complete_MAR5_lasso)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(-y)", model = "LASSO", mis_prop = 0.25)
MSE3 <- t(data.matrix(colMeans((cond3_MAR5_lasso - complete_MAR5_lasso)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVreuse", model = "LASSO", mis_prop = 0.25)
MSE4 <- t(data.matrix(colMeans((cond4_MAR5_lasso - complete_MAR5_lasso)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVsep", model = "LASSO", mis_prop = 0.25)

MSE_25lasso <- rbind(MSE1, MSE2, MSE3, MSE4)

# prop 0.75

complete_MAR7_lasso <- MAR_7_lasso20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.matrix(.,) 


cond1_MAR7_lasso <- MAR_7_lasso20[["Results_cond1"]]%>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond2_MAR7_lasso <- MAR_7_lasso20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond3_MAR7_lasso <- MAR_7_lasso20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .) %>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond4_MAR7_lasso <- MAR_7_lasso20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .) %>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)

MSE1 <- t(data.matrix(colMeans((cond1_MAR7_lasso - complete_MAR7_lasso)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(y)", model = "LASSO", mis_prop = 0.75)
MSE2 <- t(data.matrix(colMeans((cond2_MAR7_lasso - complete_MAR7_lasso)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(-y)", model = "LASSO", mis_prop = 0.75)
MSE3 <- t(data.matrix(colMeans((cond3_MAR7_lasso - complete_MAR7_lasso)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVreuse", model = "LASSO", mis_prop = 0.75)
MSE4 <- t(data.matrix(colMeans((cond4_MAR7_lasso - complete_MAR7_lasso)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVsep", model = "LASSO", mis_prop = 0.75)

MSE_75lasso <- rbind(MSE1, MSE2, MSE3, MSE4)

MSE_2575_lasso <- rbind(MSE_25lasso, MSE_75lasso)%>% select(c("model","mis_prop","cond","AUC", "brier", "sens", "spec", "cal_b0", "cal_b1", "CoxSnell", "sens_selection", "spec_selection")) 

```

```{r ridge MSE}

# prop =0.25

complete_MAR5_ridge <- MAR_5_ridge20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.matrix(.,) 


cond1_MAR5_ridge <- MAR_5_ridge20[["Results_cond1"]]%>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA)) %>% as.matrix(.,) 


cond2_MAR5_ridge <- MAR_5_ridge20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,) 


cond3_MAR5_ridge <- MAR_5_ridge20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,) 


cond4_MAR5_ridge <- MAR_5_ridge20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,) 

MSE1 <- t(data.matrix(colMeans((cond1_MAR5_ridge - complete_MAR5_ridge)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(y)", model = "ridge", mis_prop = 0.25)
MSE2 <- t(data.matrix(colMeans((cond2_MAR5_ridge - complete_MAR5_ridge)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(-y)", model = "ridge", mis_prop = 0.25)
MSE3 <- t(data.matrix(colMeans((cond3_MAR5_ridge - complete_MAR5_ridge)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVreuse", model = "ridge", mis_prop = 0.25)
MSE4 <- t(data.matrix(colMeans((cond4_MAR5_ridge - complete_MAR5_ridge)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVsep", model = "ridge", mis_prop = 0.25)

MSE_25ridge <- rbind(MSE1, MSE2, MSE3, MSE4)

# prop 0.75

complete_MAR7_ridge <- MAR_7_ridge20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.matrix(.,) 


cond1_MAR7_ridge <- MAR_7_ridge20[["Results_cond1"]]%>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond2_MAR7_ridge <- MAR_7_ridge20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond3_MAR7_ridge <- MAR_7_ridge20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .) %>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA)) %>%as.matrix(.,)


cond4_MAR7_ridge <- MAR_7_ridge20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .) %>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% as.matrix(.,)

MSE1 <- t(data.matrix(colMeans((cond1_MAR7_ridge - complete_MAR7_ridge)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(y)", model = "ridge", mis_prop = 0.75)
MSE2 <- t(data.matrix(colMeans((cond2_MAR7_ridge - complete_MAR7_ridge)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(-y)", model = "ridge", mis_prop = 0.75)
MSE3 <- t(data.matrix(colMeans((cond3_MAR7_ridge - complete_MAR7_ridge)^2, na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVreuse", model = "ridge", mis_prop = 0.75)
MSE4 <- t(data.matrix(colMeans((cond4_MAR7_ridge - complete_MAR7_ridge)^2, na.rm=T))) %>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVsep", model = "ridge", mis_prop = 0.75)

MSE_75ridge <- rbind(MSE1, MSE2, MSE3, MSE4)


MSE_2575_ridge <- rbind(MSE_25ridge, MSE_75ridge)%>% select(c("model","mis_prop","cond","AUC", "brier", "sens", "spec", "cal_b0", "cal_b1", "CoxSnell", "sens_selection", "spec_selection")) 

```

```{r table MSE}


MSE2575lr <- rbind(MSE_2575_lasso,MSE_2575_ridge) 


```



## Mean table

Lastly, in the following chunks you can find code to compute the means per condition.

```{r lasso means}

# n = 200, mis = 0.25

complete_MAR5_lasso <- MAR_5_lasso20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.matrix(.,) 


cond1_MAR5_lasso <- MAR_5_lasso20[["Results_cond1"]]%>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .) %>% as.matrix(.,) 


cond2_MAR5_lasso <- MAR_5_lasso20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.matrix(.,) 


cond3_MAR5_lasso <- MAR_5_lasso20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.matrix(.,) 


cond4_MAR5_lasso <- MAR_5_lasso20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.matrix(.,) 

meancomp <- t(data.matrix(colMeans((complete_MAR5_lasso), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "no missingness", model = "LASSO", mis_prop = 0.25)
mean1 <- t(data.matrix(colMeans(cond1_MAR5_lasso)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(y)", model = "LASSO", mis_prop = 0.25)
mean2 <- t(data.matrix(colMeans(cond2_MAR5_lasso)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(-y)", model = "LASSO", mis_prop = 0.25)
mean3 <- t(data.matrix(colMeans(cond3_MAR5_lasso)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVreuse", model = "LASSO", mis_prop = 0.25)
mean4 <- t(data.matrix(colMeans(cond4_MAR5_lasso)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVsep", model = "LASSO", mis_prop = 0.25)

mean_25lasso <- rbind(meancomp,mean1, mean2, mean3, mean4)

# prop 0.75

complete_MAR7_lasso <- MAR_7_lasso20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.matrix(.,) 


cond1_MAR7_lasso <- MAR_7_lasso20[["Results_cond1"]]%>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond2_MAR7_lasso <- MAR_7_lasso20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond3_MAR7_lasso <- MAR_7_lasso20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .) %>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond4_MAR7_lasso <- MAR_7_lasso20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .) %>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)

meancomp <- t(data.matrix(colMeans((complete_MAR7_lasso), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "no missingness", model = "LASSO", mis_prop = 0.75)
mean1 <- t(data.matrix(colMeans((cond1_MAR7_lasso), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(y)", model = "LASSO", mis_prop = 0.75)
mean2 <- t(data.matrix(colMeans((cond2_MAR7_lasso), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(-y)", model = "LASSO", mis_prop = 0.75)
mean3 <- t(data.matrix(colMeans((cond3_MAR7_lasso), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVreuse", model = "LASSO", mis_prop = 0.75)
mean4 <- t(data.matrix(colMeans((cond4_MAR7_lasso), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVsep", model = "LASSO", mis_prop = 0.75)

mean_75lasso <- rbind(meancomp, mean1, mean2, mean3, mean4)

mean_2575_lasso <- rbind(mean_25lasso, mean_75lasso)%>% select(c("model","mis_prop","cond","AUC", "brier", "sens", "spec", "cal_b0", "cal_b1", "CoxSnell", "sens_selection", "spec_selection")) 

```

```{r ridge means}



# prop =0.25

complete_MAR5_ridge <- MAR_5_ridge20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.matrix(.,) 


cond1_MAR5_ridge <- MAR_5_ridge20[["Results_cond1"]]%>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA)) %>% as.matrix(.,) 


cond2_MAR5_ridge <- MAR_5_ridge20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,) 


cond3_MAR5_ridge <- MAR_5_ridge20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,) 


cond4_MAR5_ridge <- MAR_5_ridge20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,) 

meancomp <- t(data.matrix(colMeans((complete_MAR5_ridge), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "no missingness", model = "ridge", mis_prop = 0.25)
mean1 <- t(data.matrix(colMeans(cond1_MAR5_ridge)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(y)", model = "ridge", mis_prop = 0.25)
mean2 <- t(data.matrix(colMeans(cond2_MAR5_ridge)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(-y)", model = "ridge", mis_prop = 0.25)
mean3 <- t(data.matrix(colMeans(cond3_MAR5_ridge)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVreuse", model = "ridge", mis_prop = 0.25)
mean4 <- t(data.matrix(colMeans(cond4_MAR5_ridge)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVsep", model = "ridge", mis_prop = 0.25)

mean_25ridge <- rbind(meancomp,mean1, mean2, mean3, mean4)

# prop 0.75

complete_MAR7_ridge <- MAR_7_ridge20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.matrix(.,) 


cond1_MAR7_ridge <- MAR_7_ridge20[["Results_cond1"]]%>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond2_MAR7_ridge <- MAR_7_ridge20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA))%>% as.matrix(.,)


cond3_MAR7_ridge <- MAR_7_ridge20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .) %>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0<(-4), NA))%>% mutate(cal_b0 = replace(cal_b0, cal_b0>4, NA))%>%mutate(cal_b1 = replace(cal_b1, cal_b1>10, NA)) %>%as.matrix(.,)


cond4_MAR7_ridge <- MAR_7_ridge20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .) %>%as.data.frame(.,) %>% mutate(CoxSnell = replace(CoxSnell, CoxSnell<(-4), NA))%>% as.matrix(.,)

meancomp <- t(data.matrix(colMeans((complete_MAR7_ridge), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "no missingness", model = "ridge", mis_prop = 0.75)
mean1 <- t(data.matrix(colMeans((cond1_MAR7_ridge), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(y)", model = "ridge", mis_prop = 0.75)
mean2 <- t(data.matrix(colMeans((cond2_MAR7_ridge), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-bef(-y)", model = "ridge", mis_prop = 0.75)
mean3 <- t(data.matrix(colMeans((cond3_MAR7_ridge), na.rm=T)))%>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVreuse", model = "ridge", mis_prop = 0.75)
mean4 <- t(data.matrix(colMeans((cond4_MAR7_ridge), na.rm=T))) %>% round(.,3) %>% as.data.frame(.,) %>% mutate(cond = "MI-CVsep", model = "ridge", mis_prop = 0.75)

mean_75ridge <- rbind(meancomp,mean1, mean2, mean3, mean4)


mean_2575_ridge <- rbind(mean_25ridge, mean_75ridge)%>% select(c("model","mis_prop","cond","AUC", "brier", "sens", "spec", "cal_b0", "cal_b1", "CoxSnell", "sens_selection", "spec_selection")) 

```

```{r table means}


mean2575lr <- rbind(mean_2575_lasso,mean_2575_ridge) 


```