---
title: "Plots supplementary MAR 20 n200"
author: "Paulina von Stackelberg"
date: "28 4 2021"
output: html_document
---
In this document, you can find plots generated for n=200, MAR, 20 covariates.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(facetscales)

#important: install this extension for the plots
#install.packages("remotes")
#remotes::install_github("zeehio/facetscales")
```

Choose the files; other files (and therefore other conditions) may be chosen here. The results called in this section correspond to those discussed in the main body of the manuscript.

```{r files}

MAR_1_lasso20 <- readRDS("MAR_1_lasso")
MAR_3_lasso20 <- readRDS("MAR_3_lasso")
MAR_5_lasso20 <- readRDS("MAR_5_lasso")
MAR_7_lasso20 <- readRDS("MAR_7_lasso")

MAR_1_ridge20 <- readRDS("MAR_1_ridge")
MAR_3_ridge20 <- readRDS("MAR_3_ridge")
MAR_5_ridge20 <- readRDS("MAR_5_ridge")
MAR_7_ridge20 <- readRDS("MAR_7_ridge")

```


```{r}

cond1_MAR1_lasso <- MAR_1_lasso20[["Results_cond1"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .) %>% as.data.frame(.,) %>%
  mutate(condition= 'MI-bef(y)')

cond2_MAR1_lasso <- MAR_1_lasso20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.data.frame(.,)%>%
  mutate(condition = 'MI-bef(-y)')

cond3_MAR1_lasso <- MAR_1_lasso20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'MI-CVreuse')

cond4_MAR1_lasso <- MAR_1_lasso20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'MI-CVsep')

complete_MAR1_lasso <- MAR_1_lasso20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'no missingness')

merged_data_1 <- rbind(cond1_MAR1_lasso, cond2_MAR1_lasso, cond3_MAR1_lasso, cond4_MAR1_lasso, complete_MAR1_lasso)


cond1_MAR3_lasso <- MAR_3_lasso20[["Results_cond1"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .) %>% as.data.frame(.,) %>%
  mutate(condition = 'MI-bef(y)')

cond2_MAR3_lasso <- MAR_3_lasso20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.data.frame(.,)%>%
  mutate(condition = 'MI-bef(-y)')

cond3_MAR3_lasso <- MAR_3_lasso20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition= 'MI-CVreuse')

cond4_MAR3_lasso <- MAR_3_lasso20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'MI-CVsep')

complete_MAR3_lasso <- MAR_3_lasso20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'no missingness')

merged_data_3 <- rbind(cond1_MAR3_lasso, cond2_MAR3_lasso, cond3_MAR3_lasso, cond4_MAR3_lasso, complete_MAR3_lasso)


# merge merged_data_1 and merged_data_3

merged_data_1 <- merged_data_1 %>% mutate(mis_prop = 0.25)
merged_data_3 <- merged_data_3 %>% mutate(mis_prop = 0.75)
merged_data_13_lasso<- rbind(merged_data_1, merged_data_3)%>% mutate(model = "LASSO")



```


```{r}

cond1_MAR5_lasso <- MAR_5_lasso20[["Results_cond1"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .) %>% as.data.frame(.,) %>%
  mutate(condition= 'MI-bef(y)')

cond2_MAR5_lasso <- MAR_5_lasso20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.data.frame(.,)%>%
  mutate(condition = 'MI-bef(-y)')

cond3_MAR5_lasso <- MAR_5_lasso20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'MI-CVreuse')

cond4_MAR5_lasso <- MAR_5_lasso20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'MI-CVsep')

complete_MAR5_lasso <- MAR_5_lasso20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'no missingness')

merged_data_5<- rbind(cond1_MAR5_lasso, cond2_MAR5_lasso, cond3_MAR5_lasso, cond4_MAR5_lasso, complete_MAR5_lasso)



cond1_MAR7_lasso <- MAR_7_lasso20[["Results_cond1"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .) %>% as.data.frame(.,) %>%
  mutate(condition = 'MI-bef(y)')

cond2_MAR7_lasso <- MAR_7_lasso20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.data.frame(.,)%>%
  mutate(condition = 'MI-bef(-y)')

cond3_MAR7_lasso <- MAR_7_lasso20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition= 'MI-CVreuse')

cond4_MAR7_lasso <- MAR_7_lasso20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'MI-CVsep')

complete_MAR7_lasso <- MAR_7_lasso20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'no missingness')

merged_data_7 <- rbind(cond1_MAR7_lasso, cond2_MAR7_lasso, cond3_MAR7_lasso, cond4_MAR7_lasso, complete_MAR7_lasso)


# merge merged_data_5 and merged_data_7

merged_data_5 <- merged_data_5 %>% mutate(mis_prop = 0.25)
merged_data_7 <- merged_data_7 %>% mutate(mis_prop = 0.75)
merged_data_57_lasso<- rbind(merged_data_5, merged_data_7)%>% mutate(model = "LASSO")

```



```{r}


cond1_MAR1_ridge <- MAR_1_ridge20[["Results_cond1"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .) %>% as.data.frame(.,) %>%
  mutate(condition= 'MI-bef(y)')

cond2_MAR1_ridge <- MAR_1_ridge20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.data.frame(.,)%>%
  mutate(condition = 'MI-bef(-y)')

cond3_MAR1_ridge <- MAR_1_ridge20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'MI-CVreuse')

cond4_MAR1_ridge <- MAR_1_ridge20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'MI-CVsep')

complete_MAR1_ridge <- MAR_1_ridge20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'no missingness')

merged_data_1 <- rbind(cond1_MAR1_ridge, cond2_MAR1_ridge, cond3_MAR1_ridge, cond4_MAR1_ridge, complete_MAR1_ridge)



cond1_MAR3_ridge <- MAR_3_ridge20[["Results_cond1"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .) %>% as.data.frame(.,) %>%
  mutate(condition = 'MI-bef(y)')

cond2_MAR3_ridge <- MAR_3_ridge20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.data.frame(.,)%>%
  mutate(condition = 'MI-bef(-y)')

cond3_MAR3_ridge <- MAR_3_ridge20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition= 'MI-CVreuse')

cond4_MAR3_ridge <- MAR_3_ridge20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'MI-CVsep')

complete_MAR3_ridge <- MAR_3_ridge20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'no missingness')

merged_data_3 <- rbind(cond1_MAR3_ridge, cond2_MAR3_ridge, cond3_MAR3_ridge, cond4_MAR3_ridge, complete_MAR3_ridge)


# merge merged_data_1 and merged_data_3

merged_data_1 <- merged_data_1 %>% mutate(mis_prop = 0.25)
merged_data_3 <- merged_data_3 %>% mutate(mis_prop = 0.75)
merged_data_13_ridge<- rbind(merged_data_1, merged_data_3)%>% mutate(model = "Ridge")



```


```{r}


cond1_MAR5_ridge <- MAR_5_ridge20[["Results_cond1"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .) %>% as.data.frame(.,) %>%
  mutate(condition= 'MI-bef(y)')

cond2_MAR5_ridge <- MAR_5_ridge20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.data.frame(.,)%>%
  mutate(condition = 'MI-bef(-y)')

cond3_MAR5_ridge <- MAR_5_ridge20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'MI-CVreuse')

cond4_MAR5_ridge <- MAR_5_ridge20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'MI-CVsep')

complete_MAR5_ridge <- MAR_5_ridge20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'no missingness')

merged_data_5<- rbind(cond1_MAR5_ridge, cond2_MAR5_ridge, cond3_MAR5_ridge, cond4_MAR5_ridge, complete_MAR5_ridge)


cond1_MAR7_ridge <- MAR_7_ridge20[["Results_cond1"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .) %>% as.data.frame(.,) %>%
  mutate(condition = 'MI-bef(y)')

cond2_MAR7_ridge <- MAR_7_ridge20[["Results_cond2"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>% as.data.frame(.,)%>%
  mutate(condition = 'MI-bef(-y)')

cond3_MAR7_ridge <- MAR_7_ridge20[["Results_cond3"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition= 'MI-CVreuse')

cond4_MAR7_ridge <- MAR_7_ridge20[["Results_cond4"]] %>% lapply(., FUN = function(i) do.call(rbind, i)) %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% lapply(., FUN= colMeans, na.rm=T)%>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'MI-CVsep')

complete_MAR7_ridge <- MAR_7_ridge20[["results_comp"]] %>% lapply(., FUN=function(i) sapply(i, colMeans, na.rm=T)) %>% lapply(., FUN = t) %>% do.call(rbind, .)%>%as.data.frame(.,)%>%
  mutate(condition = 'no missingness')

merged_data_7 <- rbind(cond1_MAR7_ridge, cond2_MAR7_ridge, cond3_MAR7_ridge, cond4_MAR7_ridge, complete_MAR7_ridge)


# merge merged_data_5 and merged_data_7

merged_data_5 <- merged_data_5 %>% mutate(mis_prop = 0.25)
merged_data_7 <- merged_data_7 %>% mutate(mis_prop = 0.75)
merged_data_57_ridge<- rbind(merged_data_5, merged_data_7)%>% mutate(model = "Ridge")

```

## LASSO and Ridge, cor 0

```{r}

merged_data_13_ridgeLasso <- rbind(merged_data_13_ridge, merged_data_13_lasso)

AUCBrier_13_ridgeLasso <- merged_data_13_ridgeLasso %>% 
  as.data.frame(.)%>%
  rename("Brier" = brier, "sensitivity" = sens, "specificity" = spec) %>%
  select(c("AUC", "Brier","sensitivity", "specificity",condition,mis_prop ,model)) %>%
  gather(., evaluation_measure, value, "AUC":"specificity") %>%
  mutate(condition = fct_relevel(condition, "no missingness", "MI-bef(y)", "MI-bef(-y)", "MI-CVsep", "MI-CVreuse")) %>%
  ggplot( aes(x=as.factor(mis_prop),value, fill = condition))  +
  geom_boxplot()+ xlab("Missingness proportion") + ylab("estimand value")+ scale_fill_manual(values=c("grey69", "cadetblue3" ,"darkseagreen", "chocolate", "hotpink3"), name = "MI/CV combination")+ theme_bw() + 
  facet_grid(evaluation_measure ~ model,  scales="free_y")+ theme(legend.position="bottom")+ theme(text=element_text(size=13))

AUCBrier_13_ridgeLasso


```

## LASSO and Ridge, cor 0.3
```{r}
merged_data_57_ridgeLasso <- rbind(merged_data_57_ridge, merged_data_57_lasso)

AUCBrier_57_ridgeLasso <- merged_data_57_ridgeLasso %>% 
  as.data.frame(.)%>%
  rename("Brier" = brier, "sensitivity" = sens, "specificity" = spec) %>%
  select(c("AUC", "Brier","sensitivity", "specificity",condition,mis_prop ,model)) %>%
  gather(., evaluation_measure, value, "AUC":"specificity") %>%
  mutate(condition = fct_relevel(condition, "no missingness", "MI-bef(y)", "MI-bef(-y)", "MI-CVsep", "MI-CVreuse")) %>%
  ggplot( aes(x=as.factor(mis_prop),value, fill = condition))  +
  geom_boxplot()+ xlab("Missingness proportion") + ylab("estimand value")+ scale_fill_manual(values=c("grey69", "cadetblue3" ,"darkseagreen", "chocolate", "hotpink3"), name = "MI/CV combination")+ theme_bw() + 
  facet_grid(evaluation_measure ~ model,  scales="free_y")+ theme(legend.position="bottom")+ theme(text=element_text(size=13))

AUCBrier_57_ridgeLasso

```



## 2. Plots for the calibration slope and intercept

## LASSO and Ridge, cor 0.3



```{r}
merged_data_57_ridgeLasso <- rbind(merged_data_57_ridge, merged_data_57_lasso)

scales_y <- list(
  "calibration intercept" = scale_y_continuous(limits = c(-0.2,0.4)),
  "calibration slope" = scale_y_continuous(limits = c(0, 4))
)

Cal_57_ridgeLasso <- merged_data_57_ridgeLasso %>%as.data.frame(.)   %>%rename("calibration intercept" = cal_b0,"calibration slope"= cal_b1) %>%select(c("calibration intercept", "calibration slope",condition,mis_prop ,model)) %>%gather(., evaluation_measure, value, "calibration intercept":"calibration slope") %>%mutate(condition = fct_relevel(condition, "no missingness", "MI-bef(y)", "MI-bef(-y)", "MI-CVsep", "MI-CVreuse")) %>%ggplot( aes(x=as.factor(mis_prop),value, fill = condition))  +
  geom_boxplot()+ xlab("Missingness proportion") + ylab("estimand value")+ scale_fill_manual(values=c("grey69", "cadetblue3" ,"darkseagreen", "chocolate", "hotpink3"), name = "MI/CV combination")+ theme_bw() + 
  facet_grid_sc(rows = evaluation_measure ~ model, scales = list(y = scales_y))+ theme(legend.position="bottom")+ theme(text=element_text(size=13))

Cal_57_ridgeLasso


```

## LASSO and Ridge, cor 0

```{r}
merged_data_13_ridgeLasso <- rbind(merged_data_13_ridge, merged_data_13_lasso)

scales_y <- list(
  "calibration intercept" = scale_y_continuous(limits = c(-0.2,0.4)),
  "calibration slope" = scale_y_continuous(limits = c(0, 4))
)

Cal_13_ridgeLasso <- merged_data_13_ridgeLasso %>%as.data.frame(.)   %>%
  rename("calibration intercept" = cal_b0,"calibration slope"= cal_b1) %>%select(c("calibration intercept", "calibration slope",condition,mis_prop ,model)) %>%
  gather(., evaluation_measure, value, "calibration intercept":"calibration slope") %>%
  mutate(condition = fct_relevel(condition, "no missingness", "MI-bef(y)", "MI-bef(-y)", "MI-CVsep", "MI-CVreuse")) %>%
  ggplot( aes(x=as.factor(mis_prop),value, fill = condition))  +
  geom_boxplot()+ xlab("Missingness proportion") + ylab("estimand value")+ scale_fill_manual(values=c("grey69", "cadetblue3",
  "darkseagreen", "chocolate", "hotpink3"), name = "MI/CV combination")+ theme_bw() + 
  facet_grid_sc(rows = evaluation_measure ~ model, scales = list(y = scales_y))+ theme(legend.position="bottom")+ theme(text=element_text(size=13))

Cal_13_ridgeLasso

```





## 3. Plots for sens/spec of selection

## LASSO, cor 0.3

```{r}


sens_selec_57_Lasso <-merged_data_57_lasso %>%
  mutate(condition = fct_relevel(condition, "no missingness", "MI-bef(y)", "MI-bef(-y)", "MI-CVsep", "MI-CVreuse")) %>%
  ggplot( aes(x=as.factor(mis_prop), y=sens_selection, fill = condition))+
  geom_boxplot()+ xlab("Missingness proportion") + ylab("sensitivity of selection")+
  facet_wrap(~ model)+ theme(legend.position="bottom")+ scale_fill_manual(values=c("grey69", "cadetblue3" ,"darkseagreen", "chocolate", "hotpink3"), name = "MI/CV combination")+ theme_bw()


spec_selec_57_Lasso <- merged_data_57_lasso %>%
  mutate(condition = fct_relevel(condition, "no missingness", "MI-bef(y)", "MI-bef(-y)", "MI-CVsep", "MI-CVreuse")) %>%
  ggplot( aes(x=as.factor(mis_prop), y=spec_selection, fill = condition)) +
  geom_boxplot()+ xlab("Missingness proportion") + ylab("specificity of selection")+
  facet_wrap(~ model)+ theme(legend.position="bottom")+ scale_fill_manual(values=c("grey69", "cadetblue3" ,"darkseagreen",
  "chocolate", "hotpink3"), name = "MI/CV combination")+ theme_bw()

sens_spec_selection_57 <- ggpubr::ggarrange(sens_selec_57_Lasso, spec_selec_57_Lasso, ncol=2, common.legend = TRUE, legend="bottom")


ggpubr:: ggpar(sens_spec_selection_57 ,
               font.main = c(13, "black"),
               font.x = c(13, "bold", "#2E9FDF"),
               font.y = c(13, "bold", "#E7B800"))



```


## LASSO, cor 0

```{r}


sens_selec_13_Lasso <- merged_data_13_lasso %>%
  mutate(condition = fct_relevel(condition, "no missingness", "MI-bef(y)", "MI-bef(-y)", "MI-CVsep", "MI-CVreuse")) %>%
  ggplot( aes(x=as.factor(mis_prop), y=sens_selection, fill = condition)) +
  geom_boxplot()+ xlab("Missingness proportion") + ylab("sensitivity of selection")+
  facet_wrap(~ model)+ theme(legend.position="bottom")+ scale_fill_manual(values=c("grey69", "cadetblue3" ,"darkseagreen", "chocolate", "hotpink3"), name = "MI/CV combination")+ theme_bw()


spec_selec_13_Lasso <-merged_data_13_lasso %>%
  mutate(condition = fct_relevel(condition, "no missingness", "MI-bef(y)", "MI-bef(-y)", "MI-CVsep", "MI-CVreuse")) %>%
  ggplot( aes(x=as.factor(mis_prop), y=spec_selection, fill = condition)) +
  geom_boxplot()+ xlab("Missingness proportion") + ylab("specificity of selection")+
  facet_wrap(~ model)+ theme(legend.position="bottom")+ 
  scale_fill_manual(values=c("grey69", "cadetblue3" ,"darkseagreen",   "chocolate", "hotpink3"), name = "MI/CV combination")+
  theme_bw()

spec_selec_13_Lasso

sens_spec_selection_13 <- ggpubr::ggarrange(sens_selec_13_Lasso, spec_selec_13_Lasso, ncol=2, common.legend = TRUE, legend="bottom")

ggpubr:: ggpar(sens_spec_selection_13 ,
               font.main = c(13, "black"),
               font.x = c(13, "bold", "#2E9FDF"),
               font.y = c(13, "bold", "#E7B800"))

```


## 4. Plots for Cox-Snell

## LASSO and Ridge, cor 0.3

```{r}

merged_data_57_ridgeLasso <- rbind(merged_data_57_ridge, merged_data_57_lasso)

CS_57_ridgeLasso <- merged_data_57_ridgeLasso %>%
  mutate(condition = fct_relevel(condition, "no missingness", "MI-bef(y)", "MI-bef(-y)", "MI-CVsep", "MI-CVreuse")) %>%
  ggplot( aes(x=as.factor(mis_prop), y=CoxSnell, fill = condition)) +
  geom_boxplot()+ xlab("Missingness proportion") + ylab(expression(paste("Cox-Snell ", R^2)))+
  facet_wrap(~ model)+ theme(axis.title.x = element_blank())+
  ylim(-1,0.5)+ scale_fill_manual(values=c("grey69", "cadetblue3" ,"darkseagreen", "chocolate", "hotpink3"), name = "MI/CV
  combination")+ theme_bw()+ theme(legend.position="bottom")+ theme(text=element_text(size=13))

CS_57_ridgeLasso

```



## LASSO and Ridge, cor 0

```{r}

merged_data_13_ridgeLasso <- rbind(merged_data_13_ridge, merged_data_13_lasso)

CS_13_ridgeLasso <- merged_data_13_ridgeLasso %>%
  mutate(condition = fct_relevel(condition, "no missingness", "MI-bef(y)", "MI-bef(-y)", "MI-CVsep", "MI-CVreuse")) %>%
  ggplot( aes(x=as.factor(mis_prop), y=CoxSnell, fill = condition)) +
  geom_boxplot()+ xlab("Missingness proportion") + ylab(expression(paste("Cox-Snell ", R^2)))+
  facet_wrap(~ model)+ theme(axis.title.x = element_blank())+
  ylim(-1,0.5)+ scale_fill_manual(values=c("grey69", "cadetblue3" ,"darkseagreen", "chocolate", "hotpink3"), 
  name = "MI/CV combination")+ theme_bw()+ theme(legend.position="bottom")+ theme(text=element_text(size=13))

CS_13_ridgeLasso

```
